Deep Learning

### 2015-03-24 deepreview.tex
reduced the preface to less than 100 words as requested

Deep Learning techniques allow a machine composed of multiple layers
of processing to learn to represent data, so that each layer transforms
the representation of the previous layer in a more abstract
fashion. These methods have dramatically improved the state-of-the-art
for speech recognition, object recognition, object detection,
predicting the activity of drug molecules, and many other tasks. Deep
learning discovers intricate structure in large datasets by using the
{\em backpropagation algorithm} to compute how the machine should
change in order to make less errors.  Deep {\em convolutional nets}
have brought about dramatic improvements in the processing of array
data, such as images, video, speech and audio, while {\em recurrent
  nets} have shown excellent performance for analyzing sequential
inputs and producing sequential outputs such as text and
speech. Convolutional nets have quickly become the leading technology for image
recognition and speech recognition, while recurrent nets are
competitive in several natural language processing tasks, including
language translation. Combinations of recurrent and convolutional nets
can generate good textual captions of images.

@@

\begin{figure}
\begin{center}
  \vspace{0.2cm}
  \includegraphics[width=0.70\linewidth]{convnet-diagram-labeled}
\end{center}
\vspace{-0.6cm}
\caption{The {\em outputs} (not the filters) of each layer (each column of the figure) 
of a typical convolutional network architecture
applied on the image of a handwritten digit (left). Each rectangular
image is a feature map, corresponding to the output for one of the learned features 
detected at each of the image positions.
Each column corresponds to a layer, with information flowing from the left to
the right. We see that lower level features mostly act as oriented edge detectors.
}
%\vspace{-0.8cm}
\label{fig:convnet}
\end{figure}

>>>>

Deep Learning techniques allow a machine composed of multiple processing layers
which define representations of the data that are more abstract for deeper layers.
These methods have dramatically improved the state-of-the-art
for speech recognition, object recognition, object detection,
predicting the activity of drug molecules, and many other tasks. Deep
learning discovers intricate structure in large datasets by using the
{\em backpropagation algorithm} to indicate how the machine should
change.  Deep {\em convolutional nets}
have brought about dramatic improvements to process
images, video, speech and audio, while {\em recurrent
  nets} have shone on sequential data such as text and
speech.
%Convolutional nets have quickly become the leading technology for image
%recognition and speech recognition, while recurrent nets are
%competitive in several natural language processing tasks, including
%language translation. 
%Combinations of recurrent and convolutional nets
%can generate good textual captions of images.

@@

\begin{figure}
\begin{center}
  \vspace{0.2cm}
  \includegraphics[width=0.70\linewidth]{convnet-diagram-labeled}
\end{center}
\vspace{-0.6cm}
\caption{The {\em outputs} (not the filters) of each layer (each column of the figure) 
of a typical convolutional network architecture
applied on the image of a handwritten digit (left). Each rectangular
image is a feature map, corresponding to the output for one of the learned features 
detected at each of the image positions.
Each column corresponds to a layer, with information flowing from the left to
the right. We see that lower level features mostly act as oriented edge detectors.
The last layer is fully connected so it has no spatial structure.
}
%\vspace{-0.8cm}
\label{fig:convnet}
\end{figure}
